Plug-and-play dual-tree algorithm runtime analysis

### 2015-01-14 bounds-files/sec03-approx-kde.tex
Some changes.

In the following two subsections, we will separately consider both the absolute
value approximation scheme and the relative value approximation scheme, under
the assumption of a shift-invariant kernel $\mathcal{K}(p_q, p_r) =
\mathcal{K}(\| p_q - p_r \|)$ which is monotonically decreasing and
non-negative.  In addition, we assume that there exists some bandwidth $h$ such
that $\mathcal{K}(d)$ must be concave for $d \in [0, h]$ and convex for $d \in
[h, \infty)$.  This assumption implies that the magnitude of the derivative
$|\mathcal{K}'(d)|$ is maximized at $d = h$.  These are not restrictive
assumptions; most standard kernels fall into this class, including the Gaussian,
Laplacian and Epanechnikov kernels.

@@

Next, consider the Laplacian kernel:
$\mathcal{K}_l(d) = \exp(-d / \sigma)$.  For this kernel, $h = 0$ (that is, the
kernel is always convex), so then $\mathcal{K}'_l(h) = \sigma^{-1}$.  Simple
algebraic manipulation gives $\mathcal{K}^{-1}_l(\epsilon) = -\sigma \ln
\epsilon$, resulting in $\zeta = -\mathcal{K}'_l(h) \mathcal{K}^{-1}_l(\epsilon)
\epsilon^{-1} = \epsilon^{-1} \ln \epsilon$.  So both the Laplacian and Gaussian
kernels do not exhibit dependence on the bandwidth.

To understand the lack of dependence on kernel bandwidth more intuitively,
consider that as the kernel bandwidth increases, two things happen: {\it (a)}
the reference set $R$ becomes empty at larger scales, and {\it (b)}
$\mathcal{K}^{-1}(\epsilon)$ grows, allowing less pruning at higher levels.
These effects are opposite, and for the Gaussian and Laplacian kernels they
cancel each other out, giving the same bound regardless of bandwidth.

>>>>

In the following two subsections, we will separately consider both the absolute
value approximation scheme and the relative value approximation scheme, under
the assumption of a shift-invariant kernel $\mathcal{K}(p_q, p_r) =
\mathcal{K}(\| p_q - p_r \|)$ which is monotonically decreasing and
non-negative.  In addition, we assume that there exists some bandwidth $h$ such
that $\mathcal{K}(d)$ must be concave for $d \in [0, h]$ and convex for $d \in
[h, \infty)$.  This assumption implies that the magnitude of the derivative
$|\mathcal{K}'(d)|$ is maximized at $d = h$.  These are not restrictive
assumptions; most standard kernels fall into this class, including the Gaussian,
exponential, and Epanechnikov kernels.

@@

Next, consider the exponential kernel:
$\mathcal{K}_l(d) = \exp(-d / \sigma)$.  For this kernel, $h = 0$ (that is, the
kernel is always convex), so then $\mathcal{K}'_l(h) = \sigma^{-1}$.  Simple
algebraic manipulation gives $\mathcal{K}^{-1}_l(\epsilon) = -\sigma \ln
\epsilon$, resulting in $\zeta = -\mathcal{K}'_l(h) \mathcal{K}^{-1}_l(\epsilon)
\epsilon^{-1} = \epsilon^{-1} \ln \epsilon$.  So both the exponential and Gaussian
kernels do not exhibit dependence on the bandwidth.

To understand the lack of dependence on kernel bandwidth more intuitively,
consider that as the kernel bandwidth increases, two things happen: {\it (a)}
the reference set $R$ becomes empty at larger scales, and {\it (b)}
$\mathcal{K}^{-1}(\epsilon)$ grows, allowing less pruning at higher levels.
These effects are opposite, and for the Gaussian and exponential kernels they
cancel each other out, giving the same bound regardless of bandwidth.
